Case study validations of automatic bullet matching

### 2018-10-26 index.Rmd
density curves for alnd to land comparisons

```{r why, fig.cap="Density plots for all measures "}
all_lands %>% gather(measure, score, ccf, rfscore) %>%
ggplot(aes(x = score, fill = interaction(measure, sameland))) + 
  geom_density(alpha = 0.5) +
  scale_fill_brewer(palette = "Paired") +
  facet_grid(measure~study+group1, scales="free_x") 
```

>>>>

```{r l2l, fig.cap="Density curves of similarity scores based on land-to-land comparisons for cross-correlation (top) and RF scores (bottom). Different colors indicate same source versus different source. RF scores for different source comparisons are generally well below 0.5. Some same-source comparisons are also below 0.5 for RF scores, indicating potential problems with at least one of the lands involved in the comparison."}
all_lands %>% gather(measure, score, ccf, rfscore) %>%
  mutate(
    measure = factor(measure, labels=c("Cross-correlation", "RF score"))
  ) %>%
ggplot(aes(x = score, fill = sameland, colour =sameland)) + 
  geom_density(alpha = 0.6) +
  facet_grid(measure ~ study + group1) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-land scores", limits=c(0,1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F) 
```
